\large{Vipassana for Hackers} \\ \Huge{Paper Three: Why Meditate?} \\ \large\textit{Version 0.1}

### 2019-11-28 paper-three/paper-three.tex
digestion (p3) and sample proposal formats
citation add, format update

Meditation objectively improves sleep. Black et al. found in a 2015 study that this
improvement is is not simply over the baseline, however, but also an improvement
above and beyond what can be achieved through Sleep
Hygiene Education (SHE). \cite{black2015} The difficulty with this statement, of
course, is defining the term ``meditation''. In this particular study, the meditation
in question is \textit{Mindfulness}, as taught in the UCLA Mindfulness
Course. \cite{uclamaps} Mindfulness is a very accessible form of meditation, varying
in format according to the instructor. It usually involves multiple techniques,
including \textit{Open Monitoring}, which is characterized by
openness to whatever is happening in the present moment in a variety of postures
(sitting, standing, walking, eating, etc.); \textit{Focused Attention}, which is
usually a narrow breath awareness meditation; and \textit{Loving-Kindness}, in which
meditators actively direct compassion to themselvse and others. All three of these
practices mirror the three meditation practices taught in Vipassana. However, in Vipassana, Open
Monitoring finds its parallel in objective observation of sensation internal to the
body, as we will see later.

@@

\begin{itemize}
  \item posture
  \item sleep
  \item health (activation / motivation)
  \item ethics (activation / motivation)
  \item your children: a. knowing how to meditate, b. cross-legged posture
  \item emotion (i.e. anger)
  \item mundane sphere / productivity (21 lessons, seinfeld)
  \item unlearning obsessive / repetitive thought, enhancing creativity
  \item controlling unbounded sexuality without repression (louis c.k. joke?)
  \item clarity: in thought, work, planning
  \item Die Standing Up
  \item \url{https://www.pnas.org/content/early/2019/10/18/1909959116}
\end{itemize}

@@

\bibitem{mellman2006}
  Mellman, Thomas A.
  \textit{Sleep and Anxiety Disorders}
  Psychiatric Clinics of North America, Volume 29, Issue 4, Pages 1047-1058, December 2006.
  \url{https://doi.org/10.1016/j.psc.2006.08.005}

@@

>>>>

Meditation objectively improves sleep across a number of meditation techniques.
\cite{nagendra2012} Black et al. found in a 2015 study that this
improvement is is not simply over the baseline, however, but also an improvement
above and beyond what can be achieved through Sleep
Hygiene Education (SHE). \cite{black2015} The difficulty with this statement, of
course, is defining the term ``meditation''. In this particular study, the meditation
in question is \textit{Mindfulness}, as taught in the UCLA Mindfulness
Course. \cite{uclamaps} Mindfulness is a very accessible form of meditation, varying
in format according to the instructor. It usually involves multiple techniques,
including \textit{Open Monitoring}, which is characterized by
openness to whatever is happening in the present moment in a variety of postures
(sitting, standing, walking, eating, etc.); \textit{Focused Attention}, which is
usually a narrow breath awareness meditation; and \textit{Loving-Kindness}, in which
meditators actively direct compassion to themselvse and others. All three of these
practices mirror the three meditation practices taught in Vipassana. However, in Vipassana, Open
Monitoring finds its parallel in objective observation of sensation internal to the
body, as we will see later.

@@

\begin{itemize}
  \item posture
  \item sleep
  \item digestion (``Make sure to pay attention to your poops!'' first course)
  \item diet ^
  \item schedule
  \item health (activation / motivation)
  \item ethics (activation / motivation)
  \item your children: a. knowing how to meditate, b. cross-legged posture
  \item emotion (i.e. anger)
  \item dealing with death
  \item mundane sphere / productivity (21 lessons, seinfeld)
  \item unlearning obsessive / repetitive thought, enhancing creativity
  \item controlling unbounded sexuality without repression (louis c.k. joke?)
  \item clarity: in thought, work, planning
  \item Die Standing Up
  \item \url{https://www.pnas.org/content/early/2019/10/18/1909959116}
\end{itemize}

@@

\bibitem{mellman2006}
  Mellman, Thomas A.
  \textit{Sleep and Anxiety Disorders.}
  Psychiatric Clinics of North America, Volume 29, Issue 4, Pages 1047-1058, December 2006.
  \url{https://doi.org/10.1016/j.psc.2006.08.005}

@@

\bibitem{nagendra2012}
  Nagendra R.P., Maruthai N., Kutty B.M.
  \textit{Meditation and its regulatory role on sleep.}
  Frontiers in Neurology, 3:54, April 2012.
  \url{https://doi.org/10.3389/fneur.2012.00054}
